---
title: "Choroplethr - Intro"
author: "Juanma Martinez"
date: "19/05/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# install.packages("choroplethr")
# install.packages("choroplethrMaps")
# install_github('arilamstein/choroplethrZip@v1.4.0')
# install.packages("mapproj")
    
library(choroplethr)
library(choroplethrMaps)
library(choroplethrZip)
library(mapproj)
library(ggplot2)


# View the data 

data(df_pop_state)

# show the data in the console

View(df_pop_state)

```



## Choroplethr package


New course to learn how to visualize data from the US Census Bureau’s American Community Survey (ACS), using the R package Choroplethr.

- [Choroplethr](https://www.census.gov/data/academy/courses/choroplethr.html)
- [Guide](https://cran.r-project.org/web/packages/choroplethr/choroplethr.pdf)



```{r cars, echo=FALSE, warning=FALSE}

state_choropleth(df_pop_state,
                 title  = "2012 State Population Estimates",
                 legend = "Population")
```




#### Map to show states above/below median


The following map shows what states are above or below the media population value

```{r pressure, echo=FALSE, warning=FALSE}
# 2 colors shows which states are above / below median value

state_choropleth(df_pop_state, num_colors=2, 
                 title  = "2012 State Population Estimates",
                 legend = "Population")
```




#### Map with zoom in some states


Same graph as below showing three States (California, Oregon, Washington)

```{r calm, echo=FALSE, warning=FALSE}

state_choropleth(df_pop_state, 
                 zoom = c("california", "oregon", "washington"),
                 title  = "2012 State Population Estimates - Three States",
                 legend = "Population")

```




#### Demographics dataset


Using the demographics dataset to show "State per Capita Income Estimates" for state.

```{r pressur, echo=FALSE, warning=FALSE}
data(df_state_demographics)

df_state_demographics$value = 
  df_state_demographics$per_capita_income

# Note that the state_choropleth function requires two columns:  region and value

state_choropleth(df_state_demographics,
                 num_colors = 2,
                 title  = "2013 State Per Capita Income Estimates",
                 legend = "Dollars")
```





#### New York State by country



```{r pr, echo=FALSE, warning=FALSE}

library(ggplot2)

data(df_pop_zip)

zip_choropleth(df_pop_zip, state_zoom = "new york", title="Population of New York State by county") + coord_map()

```








```{r prtr, echo=FALSE, warning=FALSE}
 data(df_pop_country)
    View(df_pop_country)
    country_choropleth(df_pop_country, "2012 World Bank Populate Estimates")

```

